---
title: "Econ 294 Final"
author: "Chenxi Zhang"
date: "March 16, 2016"
output: html_document
---


```{r package-load, include=F,message=FALSE}
library(foreign)
library(dplyr)
library(knitr)
library(stargazer)
library(RSQLite)
library(ggplot2)
library(nycflights13)
```

##Part A. Weather

```{r,echo=F,message=F,include=F}
db <- nycflights13_sqlite()
a<-left_join(
  tbl(db, "flights"),
  tbl(db, "weather"),
  by = c("year","month","day","hour"))%>% 
  collect() %>%
  mutate(canceled = is.na(arr_time))
a$month<-as.factor(a$month)
```

```{r,echo=F,warning = F,include=T}
A1.reg<-lm(dep_delay~temp+humid+wind_speed+precip+pressure+visib+wind_dir,a)
A2.reg<-lm(canceled~temp+humid+wind_speed+precip+pressure+visib+wind_dir,a)
```

```{r, warning=F,echo=F,fig.height = 3., fig.width=6}

a.plot<-ggplot(data = sample_n(a, 10000),aes(x=precip,y=dep_delay))
a.plot+geom_point()+geom_line()
```


This plot explains the relationship between departure delays and precipitation.


```{r,echo=F,header=F,results='asis'}
stargazer(A1.reg,A2.reg,header=F,type='html',title="Weather")
```



The regression results exhibit the relationship between different weather conditions with delayed and cancelled flights. 

Delay:

We can see that all of the weather condtions are statistically significant at the 99% level in determining delayed flights. 

Cancel:

Meanwhile, there are 3 conditons play no signifcant role in a cancelled flight. It includes: humidity, wind speed and  

precipitation. The other 4 conditions are statistically significant at the 99% level. 

And we can also see that the effect of precipitation plays a most significant role on the delayed flights.

We can see that if we hold all else conditions constant, precipitation increases by 1 unit 

depature delay will increase by 49.29 minetes.



##Part B Time
```{r,echo=F,warning = F,include=F}
b1.reg<-lm(dep_delay~month+day+hour,a)
b2.reg<-lm(canceled~month+day+hour,a)
```

```{r, warning=F,echo=F,fig.height = 3., fig.width=6}

a.plot<-ggplot(data = sample_n(a, 10000),aes(x=month,y=dep_delay))
a.plot+geom_point()+geom_line()

```



This plot explains the relationship between departure delays and time.


```{r,echo=F, results='asis'}
stargazer(b1.reg,b2.reg,header=F,type='html',title="time")
```



The regression results exhibit the relationship between time with delayed and cancelled flights. 

Delay:

We can see that all of the weather condtions are statistically significant at the 99% level in determining delayed flights. 

In the result, January represents constant, all of the months and hour are statistically significant in determineing delayed flights. 

Day is not statistically significant in determing delayed flights.

Cancel:

We can see that March, August, October,and November are not statistically significant in determing cancel.

Other months,day and hour are statistically significant in determing cancel.


##Part C airport destination
```{r,echo=F, message=F}
a$dest<-as.factor(a$dest)
```

```{r,echo=F,warning = F,include=T}
c1.reg<-lm(dep_delay~dest,a)
c2.reg<-lm(canceled~dest,a)

```

```{r,echo=F}
summary(c1.reg)
summary(c2.reg)
```


The regression results exhibit the relationship between airport destinations with delayed and cancelled flights. 

Delay:

The statistically significant relationships between destination and delays came from BHM,CAE,DSM,OKC,RIC,TUL,and TYS. 

These were all statistically significant at a level greater than 99%. 

Cancel:

The statistically significant relationships between destination and cancelled flights came from ALB, BDL, BGR, BHM, BNA, BWI, CAE, CHO, CHS, CLE, CMH, CVG, DAY, DCA, DSM, DTW, GRR,GSO, GSP, IAD, IND, JAC, LGA, MCI, MEM, MHT, MSP, OKC, ORD, ORF, PHL, PIT, PVD, RDU,RIC, SAV, SDF, SRQ, TUL and TYS. 

These destinations were all statistically significant at a level greater than 99%.

Other destinations don't have statistically signifcant relationships with cancelled flights.


##Part D characteristics of the plane
```{r,echo=F,warning = F,include=F}
db <- nycflights13_sqlite()


d<-left_join(
  tbl(db, "flights"),
  tbl(db, "planes"),
  by = "tailnum")%>% 
  collect() %>%
  mutate(canceled = is.na(arr_time))
```

```{r,echo=F,warning = F,include=T}
d1.reg<-lm(dep_delay~engines+seats+engine,d)
d2.reg<-lm(canceled~engines+seats+engine,d)
```

```{r, warning=F,echo=F,fig.height = 3.5, fig.width=6}

a.plot<-ggplot(data = sample_n(d, 10000),aes(x=seats,y=canceled))
a.plot+geom_point()+geom_line()

```


This plot explains the relationship between the number of seats and cancelled flights.


```{r,echo=F, results='asis'}
stargazer(d1.reg,d2.reg,header=F,type='html')
```


The regression results exhibit the relationship between characteristics of the plane with delayed and cancelled flights. 

Delay:

Only the number of seats is statistically significant in determining delay. Other characteristics are not.

And the number of seats is statistically significant at a 99% level. 

Cancel:

Only the number of seats and engines are statistically significant in determining cancelled flights. Other characteristics are not.

And the number of seats and engines are statistically significant at a 99% level. 

